Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny

### 2018-03-17 tex/manuscript.tex
commented out 5 figs that need to be added

				Length \# mm, width \# mm, length/width ratio \#, widest at anterior \# of elytra.

@@

				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

%phylogeny
\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.75\textwidth]{tree.pdf}
	\end{sideways}
	\caption{\textbf{Preferred phylogeny.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80). Characters 9, 27, 39, 45 - 47, 49, and 51 are mapped under ACCTRAN optimization; all others are unambiguously optimized. Black squares indicate non-homoplasious character state changes, whereas white squares indicate homoplasious character state changes. The numbers above and below the squares represent character numbers and states, respectively. Bremer support (upper value) and relative fit difference (lower value) values can be found at the left ends of the branches. A ``*'' symbol at the right end of a branch indicates Bootstrap support greater than 0.95.}
	\label{fig:tree}
\end{figure}

%distribution maps
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{summary.pdf}
	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
	\label{fig:map_summary}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{tylotos_ampullaceus.pdf}
	\caption{\textbf{Distributions of \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018], as indicated in the legend.}
	\label{fig:map_amptyl}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{franko.pdf}
	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
	\label{fig:map_franko}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.8\textwidth]{sculptilis.pdf}
		\end{sideways}
	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
	\label{fig:map_sculptilis}
\end{figure}
\end{document}

>>>>

				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/3 of elytra.

@@

				Length \# mm, anterior portion 1.5-2\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

				Length \# mm, anterior portion 1.75-2.25\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

				Length \# mm, anterior portion ca. 1.5\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

				Length \# mm, anterior portion 2.25-2.5\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.

@@

%phylogeny
\begin{figure}[h]
	\centering
	\begin{sideways}
		%\includegraphics[height=0.75\textwidth]{tree.pdf}
	\end{sideways}
	\caption{\textbf{Preferred phylogeny.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80). Characters 9, 27, 39, 45 - 47, 49, and 51 are mapped under ACCTRAN optimization; all others are unambiguously optimized. Black squares indicate non-homoplasious character state changes, whereas white squares indicate homoplasious character state changes. The numbers above and below the squares represent character numbers and states, respectively. Bremer support (upper value) and relative fit difference (lower value) values can be found at the left ends of the branches. A ``*'' symbol at the right end of a branch indicates Bootstrap support greater than 0.95.}
	\label{fig:tree}
\end{figure}

%distribution maps
\begin{figure}[h]
	\centering
	%\includegraphics[width=\textwidth]{summary.pdf}
	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
	\label{fig:map_summary}
\end{figure}

\begin{figure}[h]
	\centering
	%\includegraphics[width=\textwidth]{tylotos_ampullaceus.pdf}
	\caption{\textbf{Distributions of \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018], as indicated in the legend.}
	\label{fig:map_amptyl}
\end{figure}

\begin{figure}[h]
	\centering
	%\includegraphics[width=\textwidth]{franko.pdf}
	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
	\label{fig:map_franko}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		%\includegraphics[height=0.8\textwidth]{sculptilis.pdf}
		\end{sideways}
	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
	\label{fig:map_sculptilis}
\end{figure}
\end{document}
